Fisher’s Method

### 2018-08-20 Fishers_method/Fishers_method_short.Rmd
cleaned code for generating data for power tables and creating grid plots updated code for asymptotic plots

p1<-c()
dist_of_X2<-function(delta,n){
  for (j in 1:100000){ 
    p1[j]<-2*(1 - pnorm(abs(rnorm(1, delta, sqrt(2/n)))/sqrt(2/n)))
  }
  X2<--2*log(p1)
}

@@

hist(dist_of_X2(0.2,700), main=TeX('n=700, $\\theta$=0.2'), xlab=expression('X'^2))
hist(dist_of_X2(0.2,1500), main=TeX('n=1500, $\\theta$=0.2'), xlab=expression('X'^2))

hist(dist_of_X2(0.5,100), main=TeX('n=100, $\\theta$=0.5'),  xlab=expression('X'^2))
hist(dist_of_X2(0.5,250), main=TeX('n=250, $\\theta$=0.5'),  xlab=expression('X'^2))

hist(dist_of_X2(0.8,50), main=TeX('n=50, $\\theta$=0.8'),  xlab=expression('X'^2))
hist(dist_of_X2(0.8,100), main=TeX('n=100, $\\theta$=0.8'),  xlab=expression('X'^2))
```

>>>>

p1<-c()
dist_of_X2<-function(delta,n){
  for (j in 1:100000){ 
    p1[j]<-2*(1 - pnorm(abs(rnorm(1, delta, sqrt(2/n + delta^2 / (4*n))))/sqrt(2/n + delta^2 / (4*n))))
  }
  X2<--2*log(p1)
}

d1 <- as.data.frame(dist_of_X2(0.2,700))
colnames(d1)[1]<-"V1"
ggplot(d1, aes(x = V1)) +
  geom_density()

@@

hist(dist_of_X2(0.2,700), main=TeX('n=700, $\\theta$=0.2'), xlab=expression(-2*log(p_i)))
x<-seq(0,60,0.1)
curve(dnorm(x, mean = 0.5*700*2*1/4*0.2^2, sd = sqrt(2*700*1/4*0.2^2)), add = TRUE)
hist(dist_of_X2(0.2,1500), main=TeX('n=1500, $\\theta$=0.2'), xlab=expression(-2*log(p_i)))

hist(dist_of_X2(0.5,100), main=TeX('n=100, $\\theta$=0.5'),  xlab=expression(-2*log(p_i)))
hist(dist_of_X2(0.5,250), main=TeX('n=250, $\\theta$=0.5'),  xlab=expression(-2*log(p_i)))

hist(dist_of_X2(0.8,50), main=TeX('n=50, $\\theta$=0.8'),  xlab=expression(-2*log(p_i)))
hist(dist_of_X2(0.8,100), main=TeX('n=100, $\\theta$=0.8'),  xlab=expression(-2*log(p_i)))
```
